REVISITING SEMI-CONTINUOUS HIDDEN MARKOV MODELS

### 2011-09-27 misc/papers/icassp12_tied/icassp12.tex
git-svn-id: https://svn.code.sf.net/p/kaldi/code/sandbox/discrim@523 5e6a8d80-dfce-4ca6-a32a-6e07a63d50c8

\subsection{WSJ}
% TODO fix the WSJ train/dev/eval description
For the WSJ data set, we trained on the SI-284 training set, tuned on dev
and tested on eval92,93.
As the classic semi-continuous system did not yield good performance on the
RM data both in terms of run-time and performance, we omit it for the WSJ
experiments.
%
% TODO Korbinian: There are more expts ongoing, they should be done by 
%                 tomorrow! I will also fill in the details below then.
\begin{itemize}
\item
  {\em cont}: continuous triphone system using 10000 diagonal covariance
  Gaussians in 1576 tree leaves.
%\item
%  {\em semi}: semi-continuous triphone system using 768 full covariance
%  Gaussians in 2500 tree leaves, but no smoothing (explanations below).
\item
  {\em 2lvl}: two-level tree based semi-continuous triphone system using
  4096 full covariance Gaussians in 208 codebooks ( min/average/max
  components),  tree leaves, $\rho = $ and $\varrho = $.
\item
  {\em sgmm}: subspace Gaussian mixture model triphone system using a 400 
  full-covariance Gaussian background model and 2361 tree leaves.
\end{itemize}

@@

The results on the different test sets on the RM data are displayed in 
Tab.~\ref{tab:res_rm}. The classic semi-continuous system shows the worst 
performance of the four. Possible explanations are an insufficient number
of Gaussians paired overfitting of the weights to a little number of 
components. Unfortunately, this could not be eased with the interpolations
and larger numbers of Gaussians would unacceptably increase the computational 
load due to the full covariance matrices.

@@

Keeping the number of codebooks and leaves as well as the smoothing parameters
$rho$ and $\varrho$ of {\em 2lvl} constant, we experiment with the number of
Gaussians and type of covariance; the results are displayed in 
Tab.~\ref{tab:rm_diagfull}.
Interestingly, the full covariances make a strong difference: Using the same
number of Gaussians, full covariances lead to a significant improvement.
On the other hand, a substantial increase of the number of diagonal Gaussians 
leads to a similar performance as the regular continuous system.
%
Another observation from Tab.~\ref{tab:rm_diagfull} is that the smoothing
parameters need to be carefully calibrated. While the inter-iteration smoothing
helps in most cases, the intra-iteration smoothing coefficient $\rho$ strongly
depends on the type and number of Gaussians, which is due to the direct influence
of $\rho$ on the counts in Eq.~\ref{eq:intra}.

@@

% TODO Korbinian: More expts are ongoing; these include the full training set
%                 and cmvn, and hopefully a good param combination for 2lvl...
\begin{table}%[tb]
\begin{center}
\begin{tabular}{|l||c|c|c|c|c|c||c|}
\hline
~          &    dev & eval92 & eval93 & {\em avg} \\ \hline\hline
{\em cont} &        &  13.17 &  18.61 &     15.23 \\ \hline
% Korbinian: no semi-continuous for WSJ, takes too long to compute; will do it
%            for the journal, though.
%{\em semi} &        &        &        &           \\ \hline

@@

% tri2-2lvl-208-4096-6000-0-1-35-0.2 !! no cmvn !!
{\em 2lvl} &        &  12.83 &  21.61 &     16.16 \\ \hline

{\em sgmm} &        &  10.76 &  17.82 &     13.44 \\ \hline
\end{tabular}
\end{center}
\caption{\label{tab:res_wsj}
Detailed recognition results in \% WER for the '92 and '93 test sets using 
different acoustic models on the WSJ data.
}
\end{table}

% TODO Korbinian: This needs some more text once the above table is filled
The results on the different test sets on the WSJ data are displayed in
Tab.~\ref{tab:res_rm}.

>>>>

\subsection{WSJ}
% TODO fix the WSJ train/dev/eval description
%% Korbinian: For now, I inserted results on si84/half, using cmvn (tri2c),
%             the si284 take just too long for the submission.
%For the WSJ data set, we trained on the SI-284 training set, tuned on dev
%and tested on eval92,93.
To get an intuition of the performance on the WSJ data set, we trained on 
half of the SI-84 training set using settings similar to the RM experiments; 
we tested on the eval '92 and eval '93 data sets.
As the classic semi-continuous system did not yield good performance on the
RM data both in terms of run-time and performance, we omit it for the WSJ
experiments.
%
% TODO Korbinian: I hope the SI-284 experiments finish soon enough while the 
%                 submission is still open. For now, I describe SI-84/half.
\begin{itemize}
\item
  {\em cont}: continuous triphone system using 10000 diagonal covariance
  Gaussians in 1576 tree leaves.
%% TODO Korbinian: For now, I use the same setting as in RM, to evade the
%                  tuning on the dev set. Also, no semi system, too slow
%                  and bad performance on RM.
\item
    {\em 2lvl}: same configuration as for RM (no further tuning).
%\item
%  {\em 2lvl}: two-level tree based semi-continuous triphone system using
%  4096 full covariance Gaussians in 208 codebooks ( min/average/max
%  components),  tree leaves, $\rho = $ and $\varrho = $.
\item
  {\em sgmm}: subspace Gaussian mixture model triphone system using a 400 
  full-covariance Gaussian background model and 2361 tree leaves.
\end{itemize}

@@

The results on the different test sets on the RM data are displayed in 
Tab.~\ref{tab:res_rm}. The classic semi-continuous system shows the worst 
performance of the four. Possible explanations are an insufficient number
of Gaussians paired with overfitting of the weights to a little number of 
components. Unfortunately, this could not be eased with the interpolations
and larger numbers of Gaussians would unacceptably increase the computational 
load due to the full covariance matrices.

@@

Keeping the number of codebooks and leaves as well as the smoothing parameters
$\rho$ and $\varrho$ of {\em 2lvl} constant, we experiment with the number of
Gaussians and type of covariance; the results are displayed in 
Tab.~\ref{tab:rm_diagfull}.
Interestingly, the full covariances make a strong difference: Using the same
number of Gaussians, full covariances lead to a significant improvement.
On the other hand, a substantial increase of the number of diagonal Gaussians 
leads to a similar performance as the regular continuous system.
%
Another observation from Tab.~\ref{tab:rm_diagfull} is that the smoothing
parameters need to be carefully calibrated. While the inter-iteration smoothing
helps in most cases, the intra-iteration smoothing coefficient $\rho$ strongly
depends on the type and number of Gaussians, which is due to the direct influence
of $\rho$ on the counts in Eq.~\ref{eq:intra}.

@@

% TODO Korbinian: More expts are ongoing; these include the full training set
%                 and cmvn, and hopefully a good param combination for 2lvl...
\begin{table}%[tb]
\begin{center}
\begin{tabular}{|l||c|c|c|c|c|c||c|}
\hline
~          & eval '92 & eval '93 & {\em avg} \\ \hline\hline
{\em cont} &    12.75 &    17.10 &     14.39 \\ \hline % si-84/half, cmvn

@@

% tri2-2lvl-208-4096-6000-0-1-35-0.2 !! no cmvn !!
{\em 2lvl} &    12.83 &    21.61 &     16.16 \\ \hline

{\em sgmm} &    10.76 &    17.82 &     13.44 \\ \hline % si-84/half, cmvn
\end{tabular}
\end{center}
\caption{\label{tab:res_wsj}
Detailed recognition results in \% WER for the '92 and '93 test sets using 
different acoustic models on the WSJ data.
}
\end{table}

The results on the different test sets on the WSJ data are displayed in
Tab.~\ref{tab:res_rm}.
% TODO Korbinian: The following is for the si-84/half results, as currently
%                 in the table.
Using the parameters calibrated on the RM test data, the {\em 2lvl} system
performance is not as good as of the continuous or GMM systems, but still
in a similar range. Once the number of Gaussians and leaves, as well as the
smoothing parameters are tuned on the development set, we expect the error
rates to be in between the continuous and SGMM systems, as seen on the RM 
data.
